On the presentation of orthogonal groups over polynomial rings

### 2019-04-29 dl-paper.tex
Fixed Lemma 9

\subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} Throughout this subsection $\alpha$ denotes some fixed root of $\Phi$.
\begin{df} \label{defP0}
Denote by $P_\alpha(0)$ the subgroup of $\St(\Phi, R[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, R[X])$ under the
 map induced by the embedding $R[X] \subseteq R[X, X^{-1}]$:
\begin{enumerate}
 \item $z_{\beta}(Xf, g), \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
 \item $z_{\beta}(f, Xg),\ \beta \in \Phi \text{ such that }\alpha - \beta \in \Phi \cup \{0\};$
 \item $z_{\gamma}(f, g),\ \alpha \perp \gamma;$
 \item $x_{-\alpha}(X^2f),$
 \item $[x_{\beta}(m), x_{-\beta}(Xg)],\ \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi$.
\end{enumerate}
In the above formulae and below we assume that $f \in M[X]$ and $g \in R[X]$. \end{df}

Denote by $P_\alpha(*)$ the subgroup of $\St(\Phi, R[X, X^{-1}])$ generated by $P_\alpha(0)$ and the elements $x_{-\alpha}(mX)$, $m \in M$. The following lemma shows that this subgroup is sufficiently large.
\begin{lemma} The subgroup $P_\alpha(*)$ contains the image of the subgroup $\St(\Phi, R[X], XM[X])$ in $\St(\Phi, R[X, X^{-1}])$. \end{lemma}
\begin{proof}
Clearly $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, g)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $g\in R[X]$.
The assertion now easily follows from Stepanov's theorem. This can also be verified in a straightforward manner without Stepanov theorem.

Now let us verify the assertion for the generators $c_\beta(m, \xi) = [x_\beta(m), x_{-\beta}(X\xi)] = x_\beta(m) \cdot z_{\beta}(-m, -X\xi)$.
It is clear that $c_\beta(m, \xi)$ are contained in $P_\alpha(*)$ in the cases $\beta \perp \alpha$, $\alpha - \beta \in \Phi \cup \{0\}$.
There are problems: 1) for the generator $c_{-\alpha}(m, \xi)$, 2) for the generator $c_\beta(m, \xi)$, $\alpha + \beta \in \Phi$.

\begin{comment}
Let us draw the matrix for $z_\alpha(m, X\xi)$:
\[ \left(\begin{array}{cc} 1 & 0 \\ -X\xi & 1 \end{array} \right) \cdot \left(\begin{array}{cc} 1 & m \\ 0 & 1 \end{array} \right) \cdot \left(\begin{array}{cc} 1 & 0 \\ X\xi & 1 \end{array} \right) = 
 \left(\begin{array}{cc} 1 & m \\ -X\xi & 1 - mX\xi \end{array} \right) \cdot \left(\begin{array}{cc} 1 & 0 \\ X\xi & 1 \end{array} \right) = \left(\begin{array}{cc} 1 + mX\xi & m \\ -mX^2\xi^2 & 1 - mX\xi \end{array} \right) \]
Now let us draw the matrix for $c_\alpha(m, \xi)$:
\[ \left(\begin{array}{cc} 1 & m \\ 0 & 1 \end{array} \right) \left(\begin{array}{cc} 1 + mX\xi & -m \\ mX^2\xi^2 & 1 - mX\xi \end{array} \right) = 
 \left(\begin{array}{cc} 1 + mX\xi + m^2X^2\xi^2 & -m^2X\xi \\ mX^2\xi^2 & 1 - mX\xi \end{array} \right) \] 
\end{comment}
\end{proof}

>>>>

\subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} Throughout this subsection $\alpha$ denotes some fixed root of $\Phi$.
\begin{df} \label{defP0}
Denote by $P_\alpha(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, A[X])$ under the
 map induced by the embedding $A[X] \subseteq A[X, X^{-1}]$:
\begin{enumerate}
 \item $z_{\beta}(Xf, \xi), \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
 \item $z_{\beta}(f, X\xi),\ \beta \in \Phi \text{ such that }\alpha - \beta \in \Phi \cup \{0\};$
 \item $z_{\gamma}(f, \xi),\ \alpha \perp \gamma;$
 \item $x_{-\alpha}(X^2f),$
\end{enumerate}
In the above formulae and below we assume that $f \in M[X]$ and $\xi \in A[X]$. \end{df}

Denote by $P_\alpha(*)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $P_\alpha(0)$ and the elements $x_{-\alpha}(mX)$, $m \in M$. The following lemma shows that this subgroup is sufficiently large.
\begin{lemma} \label{Pstar-large} The subgroup $P_\alpha(*)$ contains the image of $K(A[X], M[X])$ in $\St(\Phi, A[X, X^{-1}])$. \end{lemma}
\begin{proof}
Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$. Invoking~\eqref{Z5} of~\cref{Zrels} with $s = Xf$, $\eta = 1$ we conclude from this that $z_{\pm\alpha}(Xf, \xi)$ also belong to $P_{\alpha}(*)$. Thus, we have shown that $P_\alpha(*)$ contains $\St(\Phi, A[X], M[X])$.

Now choose $\gamma$ to be arbitrary root orthogonal to $\alpha$. By~\cref{Kgen-strong} we are left to prove that $c_{\pm \gamma}(f, X\xi)$ lies in $P_\alpha(*)$. 
But $c_{\pm \gamma}(f, X\xi) = x_{\pm \gamma}(f) \cdot z_{\pm \gamma}(-f, -X\xi)$ is a product of two generators of type 3.
\begin{comment}
Let us draw the matrix for $z_\alpha(m, X\xi)$:
\[ \left(\begin{array}{cc} 1 & 0 \\ -X\xi & 1 \end{array} \right) \cdot \left(\begin{array}{cc} 1 & m \\ 0 & 1 \end{array} \right) \cdot \left(\begin{array}{cc} 1 & 0 \\ X\xi & 1 \end{array} \right) = 
 \left(\begin{array}{cc} 1 & m \\ -X\xi & 1 - mX\xi \end{array} \right) \cdot \left(\begin{array}{cc} 1 & 0 \\ X\xi & 1 \end{array} \right) = \left(\begin{array}{cc} 1 + mX\xi & m \\ -mX^2\xi^2 & 1 - mX\xi \end{array} \right) \]
Now let us draw the matrix for $c_\alpha(m, \xi)$:
\[ \left(\begin{array}{cc} 1 & m \\ 0 & 1 \end{array} \right) \left(\begin{array}{cc} 1 + mX\xi & -m \\ mX^2\xi^2 & 1 - mX\xi \end{array} \right) = 
 \left(\begin{array}{cc} 1 + mX\xi + m^2X^2\xi^2 & -m^2X\xi \\ mX^2\xi^2 & 1 - mX\xi \end{array} \right) \] 
\end{comment}
\end{proof}
